### 2022-06-13 paper.tex
moved package description behind benchmark
a few more changes

@@

\section{Benchmarks}
To assess performance of our methods, we obtained two previously published scBS-Seq data sets and re-analysed them with \texttt{scbs}.

To assess the impact of our methods on dimensionality reduction and the ability to distinguish different (sub)types of cells, we used a data set from \citet{luo2017single}. This data set consists of 3377 single-cell CpG methylomes from the murine frontal cortex, comprising 16 neuronal subtypes.
We subjected this data set to the standard scBS workflow: defining a set of genomic intervals, quantifying methylation in these intervals, and subjecting the resulting matrix to PCA.
We repeated this analysis several times, either using 100~kb tiles or VMRs, and either using methylation fractions or mean shrunken residuals as a measure of methylation. \todo{Is the following correct?} For both types of regions, the 100~kb tiles and the VMRs, we ranked the regions by the number of covering cells (i.e., cells with at least on read in the region) and keep only the top 1000 regions.

Since some scBS protocols are based on the use of 96-well-plates, and since scBS is costly and labor-intensive, only few laboratories are currently able to obtain thousands of single cell methylomes.
To simulate a smaller data set, we subsampled the frontal cortex data set to 500 cells and repeated our analysis.
Here, our approach keeps its good score, while the simple approach falls behind (Figure \ref{figure:score}B).

>>>>

\section{Benchmarks}

To demonstrate the value of our proposed improvements, we obtained two previously published sc-BS-Seq data sets and re-analysed them.

To assess the impact of our methods on dimensionality reduction and the ability to distinguish different (sub)types of cells, we used a data set from \citet{luo2017single}. This data set consists of 3377 single-cell CpG methylomes from the murine frontal cortex, comprising 16 neuronal subtypes.
We subjected this data set to the standard scBS workflow: defining a set of genomic intervals, quantifying methylation in these intervals, and subjecting the resulting matrix to PCA.
We repeated this analysis several times, either using 100~kb tiles or VMRs, and either using methylation fractions or mean shrunken residuals as a measure of methylation. \todo{Is the following correct?} For both types of regions, the 100~kb tiles and the VMRs, we ranked the regions by the number of covering cells (i.e., cells with at least on read in the region) and kept only the top 100, 1000, or 10,000 regions.

Since sc-BS-Seq protocols is still rather costly and labor-intensive, only few laboratories are currently able to obtain thousands of single cell methylomes.
To simulate a smaller data set, we subsampled the frontal cortex data set to 500 cells and repeated our analysis.
Here, our approach keeps its good score, while the simple approach falls behind (Figure \ref{figure:score}B).

@@
